\documentclass[11pt,letterpaper,sans,unicode]{moderncv}
\usepackage{xpatch}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{enumitem}
\usepackage{relsize}
\usepackage{textcomp}
\usepackage{units}
\usepackage{lineno}
\usepackage{rotating}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{xcolor}
\usepackage[gen]{eurosym}
\usepackage{comment}
\usepackage{etaremune}

%\usepackage[T1]{fontenc}
%\usepackage{hyperref}
%\usepackage[latin9]{inputenc}


\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=0.7in,bottom=0.7in,left=1in,right=1in,bindingoffset=0cm]{geometry}
\setlength{\hintscolumnwidth}{3cm}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{lastpage}
\usepackage{mathabx}
\cfoot{{\color{gray} Page \thepage\ of \pageref{LastPage}}}

\def\baas{{Bulletin of AAS}}               % Bulletin of the AAS
\def\prd{{Phys. Rev.} D}
\def\prl{{Phys.Rev.} Lett}
\def\ajp{{Amer. J. Phys}}
\def\apjl{{Astrophys. J.} Lett}
\def\apjs{{Astrophys. J.} Supp}
\def\apj{{Astrophys. J.}}
\def\cqg{{Class. Quantum Grav.}}
\def\aaps{{A\&AS}}
\def\pasj{{PASJ}}
\def\mnras{{MNRAS}}
\def\aapr{{A\&ARv}}
\def\aap{{A\&A}}
\def\grg{{Gen. Rel.\&Grav.}}
\def\na{{New Astronomy}}
\def\ptp{{Progress of Theoretical Physics}}
\def\araa{{ARA\&A}}
\def\ssr{{Space Sci. Rev.}}
\def\jpcs{{J. Phys. Conf. Ser.}}
\def\npb{{Nucl. Phys. B}}
\def\clrpaawp{{Can. Lon. Ran. Plan A\&A}}


\newcommand{\cvreference}[9]{%
  \textbf{#1}\newline% Name
  \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
  \ifthenelse{\equal{#3}{}}{}{#3\newline}%
  \ifthenelse{\equal{#4}{}}{}{#4\newline}%
  \ifthenelse{\equal{#5}{}}{}{#5\newline}%
  \ifthenelse{\equal{#6}{}}{}{#6\newline}%
  \ifthenelse{\equal{#7}{}}{}{#7\newline}%
  \ifthenelse{\equal{#8}{}}{}{\emailsymbol~{\footnotesize \texttt{\emaillink[]{#8}}}\newline}
  \ifthenelse{\equal{#9}{}}{}{\phonesymbol~#9}
  }


%%%%%% My Macros %%%%%
\newcommand{\editem}[7]{\cventry{#1}{\hspace{4mm}#2 \vspace*{1mm}}{#3}{#4}{}{\hspace{4mm}\textbf{Advisor:} #5}{\hspace{4mm}\textbf{#6:} \textit{#7} }}
%School City/State, School, Degree, Degree Date, Advisor, title type, title

\newcommand{\bsitem}[4]{\cventry{#1}{\hspace{4mm}#2 \vspace*{1mm}}{#3}{#4}{}{}{}}
%School City/State, School, Degree, Degree Date

\newcommand{\pubitem}[4]{\item \cvitem{}{\textit{#1}.\\ {#2} \\{\color{color1} \href{#3}{\color{color1} #4}} }\vspace{-0.3cm}} %title, authors, href, journal %\textcolor{red}{$\bullet$} $141$ citations.

\newcommand{\software}[3]{\cventry{}{\bbullet #2}{\hspace{2mm}\texttt{#1}}{}{}{\bbullet \color{color1} \url{#3}}} %Name, Description, URL
%\vspace{-0.1cm}

\newcommand{\talkitem}[3]{\item \textit{#1}\\{#2}, #3} %Title, Meeting, Date
\newcommand{\invtalkitem}[3]{\item \textbf{#1}, \hfill{#2} \\ \textit{\color{color1}``#3''} \vspace{-0.1cm}} %Place, Title, Date

%\newcommand{\invtalkitem}[3]{\cvitemwithcomment{}{\item #1 \color{color1}\textit{``#2''}}{#3} \vspace{-0.1cm}}
\newcommand{\outtalkitem}[4]{\cvitemwithcomment{}{\bbullet #1, #2 \color{color1}\textit{``#3''}}{#4} \vspace{-0.1cm}} %What, Where, Title, Year
\newcommand{\studentitem}[4]{\item \textit{#1}, {#2} \hfill{#3} \\ \textit{``#4''} } %Name, School, Date, Title\vspace{-0.1cm}
\newcommand{\confitem}[2]{\item #1 \hfill #2} %Meeting, Date

\newcommand{\blucirc}{{\color{color1} $\circ\;\;$}}
\newcommand{\bbullet}{\hspace{0.4cm}\blucirc}

\input{contact}
%\definecolor{color1}{HTML}{1f77b4}
%\hypersetup{urlcolor=color1,linkcolor=color1}
\title{Biosketch}
\begin{document}
\makecvtitle

\vspace{-13mm}
%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}

\cventry{September 2022--Present}{\hspace{0.4cm}{\blucirc}Assistant Professor of Physics}
{\textsc{Oregon State University}}
{Corvallis, OR}{}{} %\vspace{-6mm}
%

\cventry{August 2018--September 2022}{\hspace{0.4cm}{\blucirc}NANOGrav Physics Frontiers Center Senior Postdoctoral Fellow}
{\textsc{University of Washington Bothell}}
{Bothell, WA}{}{} %\vspace{-6mm}
%
\cventry{August 2016--July 2018}{\hspace{0.4cm}{\blucirc}NANOGrav Physics Frontiers Center Postdoctoral Fellow}{\textsc{University of Texas Rio Grande Valley}}{Brownsville, TX}{}{} %\vspace{-6mm}
%
\cventry{August 2015--July 2016}{\hspace{0.4cm}{\blucirc}Visiting Assistant Professor}{\textsc{Hendrix College}}{Conway, AR}{}{}
%
\cventry{September 2014 - August 2015}{\hspace{0.4cm}{\blucirc}Postdoctoral Teaching Position/ Head Online Class Developer}
{\textsc{Utah State University}}{Logan, UT}{}{}
%
\cventry{June 2012 - May 2013}{\hspace{0.4cm}{\blucirc}Visiting Scholar, Center for Relativistic Astrophysics}
{\textsc{Georgia Institute of Technology}}{Atlanta, GA}{}{}
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------
%\vspace{-3mm}
\section{Education}
%School City/State, School, Degree, Degree Date, Advisor, title type, title

\editem{Logan, Utah}{Utah State University}{PhD in Physics}{December 2014}{Dr.~James~T.~Wheeler}{Dissertation Title}{Conformal gravity and time}
\vspace{2mm}

\editem{Corvallis, Oregon}{Oregon State University}{MS Physics  (Mathematics Minor)}{June 2008}{Dr.~Tevian~Dray}{Thesis Title}{The effects of negative-energy shells on Schwarzschild spacetime}
\vspace{2mm}

\bsitem{Syracuse, New York}{State University of New York, College of Environmental Science and Forestry}{BS Biology}{December 1999}

%----------------------------------------------------------------------------------------
%   GRANTS & FUNDING
%----------------------------------------------------------------------------------------

\section{Grants \& Funding}
\input{grants}

\section{Awards}
\input{awards}

%\vspace{-3mm}
\section{Media Engagement, Outreach \& Diversity}

%\begin{comment}
\subsection{Media Coverage \& Engagement}

\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://physics.oregonstate.edu/impact/2024/02/nsf-career-award-helps-physicist-unravel-the-mysteries-of-the-universe}{``\textit{NSF Career Award helps physicist unravel the mysteries of the universe}''}}}{Feb 2023} \vspace{-0.1cm}
\hspace{0.71cm} OSU College of Science  \\
%
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://www.youtube.com/watch?v=U65mWdH3nV0}{``\textit{Physicist Answers Physics Questions From Twitter | Tech Support | WIRED}''}}}{Nov 2023} \vspace{-0.1cm}
\hspace{0.71cm} WIRED Magazine  \\
%
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://www.npr.org/transcripts/1183878163}{``\textit{Scientists have found signs of a new kind of gravitational wave. It's really big}''}}}{June 2023} \vspace{-0.1cm}
\hspace{0.71cm} National Public Radio, Morning Edition  \\
%
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://www.pbs.org/newshour/show/gravitational-wave-discovery-leads-to-greater-understanding-of-the-fabric-of-our-universe}{``\textit{Gravitational wave discovery leads to greater understanding of the fabric of our universe}''}}}{June 2023} \vspace{-0.1cm}
\hspace{0.71cm} PBS News Hour \\
%
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://www.reuters.com/science/scientists-discover-that-universe-is-awash-gravitational-waves-2023-06-29/}{``\textit{Scientists discover that universe is awash in gravitational waves}''}}}{June 2023} \vspace{-0.1cm}
\hspace{0.71cm} Reuters Wire Service  \\
%
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://www.geekwire.com/2023/evidence-hum-gravitational-waves/}{``\textit{Astrophysicists report solid evidence for a background hum of gravitational waves}''}}}{June 2023} \vspace{-0.1cm}
\hspace{0.71cm} GeekWire  \\
%
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://today.oregonstate.edu/news/astrophysics-collaboration-led-oregon-state-finds-chorus-gravitational-waves}{``\textit{Astrophysics collaboration led by Oregon State finds 'chorus' of gravitational waves}''}}}{June 2023} \vspace{-0.1cm}
\hspace{0.71cm} OSU press release  \\

%\end{comment}
\subsection{Outreach Projects}
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://astronomyontap.org/locations/corvallis-or/}{\textit{Astronomy on Tap Corvallis Lecture Series}}}}{Fall 2023 -- Present} \vspace{-0.1cm}
\hspace{0.71cm} Bombs Away Cafe, First Tuesday of the Month  \\
\hbox{\hspace{0.71cm} 300+ Attendees and counting}

\subsection{Outreach Talks}
\renewcommand\labelenumi{\bfseries\theenumi .}
\small
\outtalkitem{Astronomy on Tap Speaker}{}{Black Holes}{2024}
\outtalkitem{Academy for Lifelong Learning}{}{Whispers of Behemoth Black Holes}{2024}
\outtalkitem{Science Pub}{}{ The Search for Lumbering Giants: Whispers of Behemoth Black Holes}{2024}
\outtalkitem{North City Tech Meetup}{}{Searching for Gravitational Waves with a Galactic-Scale Detector}{2021}
\outtalkitem{Gravitational Wave Astronomy}{Eastside Preparatory}{How are gravitational waves detected?}{2020}
%\outtalkitem{Science Wednesday Panel Discussion}{King's Live Music}{The Science of Time Travel}{2015}
%\outtalkitem{Science Fiction Club Talk}{Hendrix College}{Black Holes and Wormholes}{2015}
%\outtalkitem{Science Unwrapped (500 person public lecture)}{Utah State University}{Explore to Conserve}{2013}
%\outtalkitem{Conservation Club Talk}{Weber State}{A Scientist's Role in Conservation}{2012}
%\outtalkitem{Science Unwrapped}{Swaner Ecocenter}{A Scientist's Role in Modern Exploration}{2012}
%\outtalkitem{Cache Valley Stargazers Talk}{Logan, UT}{Black Holes: Ninjas of the Night Sky}{2009}

\subsection{Diversity \& Equity}
\begin{itemize}[leftmargin=8mm]
\item Member, College of Science Equity, Access and Inclusion Leadership Council, 2023 -- Present
\item Appointee, NANOGrav Equity and Climate Committee, 2023 -- Present
\item Member APS Climate Site Visit Committee, 2024
\item Chair/Member, Diversity, Inclusion, Culture \& Equity Committee, OSU Physics Depart, 2022 -- 2024

\item Founding Co-chair, DEI Working Group,  {\color{color1} \href{https://indico.ego-gw.it/event/29/sessions/53/attachments/420/685/International_Gravitational-Wave_Outreach_Group_Meeting__Briefing_Document.pdf}{International Gravitational Outreach Group}}, 2018-- 2021
\item Member of the NANOGrav chapter of the {\color{color1} \href{https://www.aps.org/programs/innovation/fund/idea.cfm}{APS Inclusion, Diversity, \& Equity Alliance}}, 2020-- 2022
\item Local Organizing Committee, UW, Seattle (2019) {\color{color1} \href{https://www.aps.org/programs/women/cuwip/cuwiphistory.cfm}{Conferences for Undergraduate Women in Physics}}
%\item As an LOC member for the Spring 2018 NANOGrav collaboration meeting at UW Bothell, I coordinated with the Bothell Center for Diversity on a seminar to promote allyship, inclusiveness, and equity within the NANOGrav collaboration.
\end{itemize}


\end{document}
